Approximation as Differentiation

### 2025-05-04 appendix/notes/fam.tex
Minor tweaks.
Switch to contravariant formulation.

\begin{definition}[Reindexing]
For any $f: I \to J$ define the \emph{reindexing} functor $\reindex{-}{f}: \Fam(J,\cat{C}) \to
\Fam(I,\cat{C})$ which:
\begin{itemize}
\item sends any $J$-indexed family $X$ to the $I$-indexed family $\reindex{X}{f}$ where $\reindex{X}{f}_i =
X_{f(i)}$ for any $i \in I$;
\item sends any morphism $g: X \to Y$ between $J$-indexed families to the morphism $\reindex{g}{f}:
\reindex{X}{f} \to \reindex{X}{g}$ where $\reindex{g}{f}_i = g_{f(i)}$.
\end{itemize}
\end{definition}

\begin{definition}
Then define $\Fam(-,\cat{C}): \Set^{\op} \to \Cat$ to be the functor which sends any set $I$ to
$\Fam(I,\cat{C})$ and any function $f: I \to J$ to the functor $\reindex{-}{f}: \Fam(J,\cat{C}) \to
\Fam(I,\cat{C})$.
\end{definition}

>>>>

\begin{definition}[Reindexing]
For any $f: I \to J$ define the \emph{reindexing} functor $\reindex{-}{f}: \Fam(J,\cat{C}) \to
\Fam(I,\cat{C})$ which:
\begin{itemize}
\item sends any $J$-indexed family $X$ to the $I$-indexed family $\reindex{X}{f}$ where $\reindex{X}{f}_i =
X_{f(i)}$ for any $i \in I$;
\item sends any morphism $g: X \to Y$ between $J$-indexed families to the morphism $\reindex{g}{f}:
\reindex{X}{f} \to \reindex{Y}{f}$ where $\reindex{g}{f}_i = g_{f(i)}$.
\end{itemize}
\end{definition}

By \emph{indexed category over $\cat{C}$} we shall mean any functor $\cat{C}^\op \to \Cat$.

\begin{definition}
Then define $\Fam(-,\cat{C}): \Set^{\op} \to \Cat$ to be the indexed category which sends any set $I$ to
$\Fam(I,\cat{C})$ and any function $f: I \to J$ to the functor $\reindex{-}{f}: \Fam(J,\cat{C}) \to
\Fam(I,\cat{C})$.
\end{definition}

### 2025-05-04 appendix/notes/grothendieck.tex
Switch to contravariant formulation.

By an \emph{indexed category over $\cat{C}$} we shall mean a functor $\cat{C}^\op \to \Cat$.

\begin{definition}[Grothendieck construction for $F$]
Suppose an indexed category $T: \cat{C}^\op \to \Cat$. The \emph{Grothendieck construction}
for $T$ is the category $\Grothendieck{}T$ which has:
\begin{itemize}
\item as objects, all pairs $(X, \partial X)$ of an object $X$ of $\cat{C}$ and an object $\partial X$ of $F(X)$;
\item as morphisms $(X, \partial X) \to (Y, \partial Y)$ all pairs $(f, \partial f)$ of morphisms $f: X
\to Y$ in $\cat{C}$ and morphisms $\partial f: F(X)(\partial X) \to \partial Y$ in $F(Y)$.
\end{itemize}
\end{definition}

\noindent When $F$ is contravariant, a morphism $f: X \to Y$ in $\Grothendieck{\cat{C}}{F}$ is a morphism
$\idx{f}: \idx{X} \to \idx{Y}$ in $\cat{C}$ paired with a morphism $\faml{f}: \faml{X} \to
F(\idx{f})(\faml{Y})$ in $F(\idx{X})$. \todo{Might want to unpack this a bit.}

\begin{definition}[Category of families]
For any category $\cat{C}$ define $\Fam(\cat{C})$ to be the Grothendieck construction
$\Grothendieck{\Set^{\op}}\Fam(-,\cat{C})$.
\end{definition}

\noindent In $\Fam(\cat{C})$ the objects $X$ are thus sets $\idx{X}$ paired with indexed families $\faml{X}$
in $\Fam(\idx{X},\cat{C})$ and morphisms $f: X \to Y$ are functions $\idx{f}: \idx{X} \to \idx{Y}$ paired with
morphisms $\faml{f}: \faml{X} \to \reindex{\faml{Y}}{\idx{f}}$ in $\Fam(\idx{X},\cat{C})$.

>>>>

\begin{definition}[Grothendieck construction for $F$]
Suppose an indexed category $T: \cat{C}^\op \to \Cat$. The \emph{Grothendieck construction}
for $T$ is the category $\Grothendieck{}T$ which has:
\begin{itemize}
\item as objects, all pairs $(X, \partial X)$ of an object $X$ of $\cat{C}$ and an object $\partial X$ of $F(X)$;
\item as morphisms $(X, \partial X) \to (Y, \partial Y)$ all pairs $(f, \partial f)$ of morphisms $f: X
\to Y$ in $\cat{C}$ and morphisms $\partial f: \partial X \to F(Y)(\partial Y)$ in $F(X)$.
\end{itemize}
\end{definition}

\subsubsection{Category of families}

\begin{definition}[Category of families]
For any category $\cat{C}$ define $\Fam(\cat{C})$ to be the Grothendieck construction
$\Grothendieck{}\Fam(-,\cat{C})$.
\end{definition}

\noindent In $\Fam(\cat{C})$ the objects $(X, \partial X)$ are thus sets $X$ paired with indexed families
$\partial X$ in $\Fam(X,\cat{C})$ and morphisms $(f, \partial f): (X, \partial X) \to (Y, \partial Y)$ are
functions $f: X \to Y$ paired with morphisms $\partial f: \partial X \to \reindex{\partial Y}{f}$ in
$\Fam(X,\cat{C})$.
